Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-13 paper.tex
Better symbol definitions; closes #51

The behavior of the mean rotor drag coefficient is similar, though the changes
are less dramatic. This is likely due to cross-flow turbine geometry, where
increases in blade drag at lower $Re$ somewhat offsets the reduction in lift, to
keep total streamwise force from changing as much as the rotor torque. The
tendency for $C_D$ to continue increasing with $Re$ may also include the effects
of an increasing Froude number, which increases free surface deformation and
wave drag during towing without increasing flow through the turbine.

@@

Results from the XFOIL calculations are shown in Figure~\ref{fig:foil-Re-dep},
where values of maximum lift coefficient, minimum drag coefficient, and maximum
lift-to-drag ratio are normalized (for comparison between foils) and plotted
versus $Re_c$. In general, larger camber is associated with decreased foil
performance at lower Reynolds number. The data and processing code for these
calculations is available from \cite{Bachant2015-NACAXX20-XFOIL}.

>>>>

The behavior of the mean rotor drag coefficient $C_D$ is similar, though the
changes are less dramatic. This is likely due to cross-flow turbine geometry,
where increases in blade drag at lower $Re$ somewhat offsets the reduction in
lift, to keep total streamwise force from changing as much as the rotor torque.
The tendency for $C_D$ to continue increasing with $Re$ may also include the
effects of an increasing Froude number, which increases free surface deformation
and wave drag during towing without increasing flow through the turbine.

@@

Results from the XFOIL calculations for the airfoil profiles are shown in
Figure~\ref{fig:foil-Re-dep}, where values of maximum lift coefficient
$C_{l_{\max}}$, minimum drag coefficient $C_{d_{\min}}$, and maximum
lift-to-drag ratio are normalized (for comparison between foils) and plotted
versus $Re_c$. In general, larger camber is associated with decreased foil
performance at lower Reynolds number. The data and processing code for these
calculations is available from \cite{Bachant2015-NACAXX20-XFOIL}.
